Paper 1

### 2022-05-29 scripts/Paper 1.Rmd
u

rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
rainfall.SP$Site <- "SP"

rainfall <- rbind(rainfall_L, rainfall.SP)
rainfall$month <- as.factor(rainfall$month)

@@

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_point(aes(color = Year, size = 2)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()

>>>>

rainfall.SP <- input.daily %>% select(Precip, jday, month, Year)
rainfall.SP$Site <- "SP"
rainfall.SP$date <- as.Date(with(rainfall.SP, paste(Year, month, jday,sep="-")), "%Y-%m-%j")
rainfall.2merge <- rainfall_L %>% filter(Year == 2019  & jday >= 244 & jday < 354)

rainfall <- rbind.fill(rainfall.2merge, rainfall.SP)
rainfall$month <- as.factor(rainfall$month)

@@

rainfall.summary %>% 
  ggplot(., aes(x = month, y = monthly.sum, group = Year, fill = Site)) +
  geom_col(position = "dodge", aes(fill = Year)) + 
  ylab("Monthly rainfall (mm)")+
  xlab("month")+
  theme_classic()
```
